---
title: "HILICNeg_skyline_BMIS"
author: "Angie Boysen"
date: "Nov 03, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyr)
require(graphics); require(grDevices)
library(Hmisc)
library(gtools)
library(cowplot)
require(RColorBrewer)
library(readr)
library(plotly)
library(stringr)
library(GGally)
library(dplyr)
require(readr)
library(lattice)
library(stats)
library(scales)
```

## Import Data
Data should have been exported as "alignement results" area
```{r importdata, message=FALSE, warning=FALSE}

column.id = "HILICNeg"
filename <- "../output/TargetedMetabolites/HILICNeg_QC_skyline_IS_data.csv"
dat <- read_csv(filename) 

IS <- dat %>%
  filter(`Protein Name` == "Internal Standards"|
           `Protein Name`=="Internal Standards_neg")
glimpse(IS)
```

## basic QC
just ditch anything that doesn't have a perfect score in the flags
```{r basic QC, echo=FALSE, message=FALSE, warning=FALSE}
filtered.dat <- dat %>%
  filter(all.flags=="all ok" | is.na(all.flags))
```

## Read in Internal Standard data, add in injec_volume data from Sample Key
```{r Output a summery of filtered results, echo=FALSE, message=FALSE, warning=FALSE}
IS.dat <- IS %>%
  select(`Replicate Name`, `Precursor Ion Name`, Area) %>%
  dplyr::rename(MassFeature = `Precursor Ion Name`) %>%
  mutate(Area = as.numeric(Area),
         MassFeature = paste(MassFeature, "- IS"))

SampKey <- read_csv("../RawData/HILIC Sample List.csv") %>%
  filter(`Replicate Name` %in% IS.dat$`Replicate Name`) %>%
  select(`Replicate Name`, dilution) %>%
  filter(!is.na(dilution))%>%
  mutate(MassFeature = "Dil.Factor",
         Area = dilution) %>%
  select(`Replicate Name`, Area, MassFeature)

IS.dat <- rbind(IS.dat, SampKey)
glimpse(IS.dat)
```

Look at extraction replication of the Internal Standards If things don't look good with some IS or certain samples, make sure to fix them or at least not include them as possibilities for normalization
```{r glimpse IS, message=FALSE, warning=FALSE}
ggplot(IS.dat %>% 
         filter(!grepl("Std",`Replicate Name`)),
       aes(x=`Replicate Name`, y=Area)) + 
  geom_bar(stat="identity") + 
  facet_wrap( ~MassFeature, scales="free_y")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1,vjust = 0.5, size = 5), 
        axis.text.y = element_text(size = 7),
        legend.position = "top",
        strip.text = element_text(size = 7))+
  ggtitle("IS Raw Areas")
```

Edit IS data if necessary Optional if there are certain IS that aren't trustworthy
Take out GBT here because that was added to the incubations
```{r Edit IS data, message=FALSE, warning=FALSE}
IS.dat <- IS.dat %>%
  filter (MassFeature != "Betaine, 13C5-15N - IS")# %>%
  # filter (MassFeature != "Heavy Succinic Acid")%>%
  # filter (MassFeature != "DL-Histidine, 15N")
```

##Get untargeted data into long format
```{r make data long format, message=FALSE, warning=FALSE}
IS.dat <- IS.dat 
replicates <- unique(IS.dat$`Replicate Name`) #Only use this if you have numbers at the beginning of runs

filtered.dat.long <- filtered.dat %>%
  rename(MassFeature = `Precursor Ion Name`) %>%
  filter(`Replicate Name` %in% replicates) %>%
  dplyr::select(MassFeature, `Replicate Name`, Area)
glimpse(filtered.dat.long)
```
#Rename Runs - optional chunk to adjust the naming of individual runs ##EDIT This if your names do not follow the exact structure Name structure must be: Date_type_ID_replicate
```{r, message=FALSE, warning=FALSE}
# filtered.dat.long <- filtered.dat.long %>%
#   mutate(`Replicate Name` = `Replicate Name` %>%
#             str_replace("_Blk_Blk_M","_Blk_M")%>%
#             str_replace("ExtractsFull_","Extracts_Full")%>%
#            str_replace("ExtractsHalf_","Extracts_Half"))

# IS.dat <- IS.dat %>%
#   mutate(`Replicate Name` = `Replicate Name` %>%
#            str_replace("17","X17") %>%
#             str_replace("_Blk_Blk_M","_Blk_M")%>%
#            str_replace("ExtractsFull_","Extracts_Full")%>%
#            str_replace("ExtractsHalf_","Extracts_Half"))

print(unique(filtered.dat.long$`Replicate Name`))
```

#Calculate mean values for each IS
```{r get mean values for IS, message=FALSE, warning=FALSE}
IS.means <- IS.dat %>%
  filter(!grepl("_Blk", `Replicate Name`)) %>%
    filter(!grepl("_Std", `Replicate Name`),
           !grepl("QC2",`Replicate Name`)) %>%
  mutate(MassFeature = as.factor(MassFeature))%>%
     group_by(MassFeature) %>%
     summarise(ave = mean(Area)) %>%
  mutate(ave = ifelse(MassFeature=="Dil.Factor",1,ave))
head(IS.means)
write_csv(IS.means, paste0("../output/TargetedMetabolites/",column.id, "_IS Means.csv"))
```

#Normalize to each internal Standard 
Actually scaling/adjusting by dividing by IS peak area and multiplying by the average IS peak area. Output is a dataframe 'area.norm' that has each peak adjusted to each possible internal standards
```{r do the normalization, message=FALSE, warning=FALSE}
binded <- rbind(IS.dat, filtered.dat.long) %>%
  unique()
wArea<- binded %>% 
     select(`Replicate Name`, MassFeature, Area) %>%
     spread(key=MassFeature, value=Area) %>%
     as.data.frame

IS.list <- unique(IS.dat$MassFeature)
this.IS <- IS.list[1]
area.norm <- wArea[,-1] %>% 
          sapply(FUN = function(x) x/wArea[,grep(this.IS,
                                                 names(wArea))]) %>%
          as_data_frame %>% mutate(`Replicate Name` = wArea$`Replicate Name`) %>%
          gather(MassFeature,Area_Norm, -`Replicate Name`)
this.mean <- IS.means %>% filter(MassFeature==this.IS) %>% 
     select(ave) %>% as.numeric
area.norm <- area.norm %>% mutate(Area_Norm = Area_Norm*this.mean)
key <- ncol(area.norm)
count <- length(which(!is.na(area.norm$Area_Norm)))/
               length(unique(area.norm$`Replicate Name`))
names(area.norm)[key] <- paste(this.IS,"Norm.Area",sep=".")
print(paste(1, this.IS, count, sep="-"))
for (i in 2:length(IS.list)){
     this.IS <- IS.list[i]
     if(length(wArea[,grep(this.IS, names(wArea))])!=0){
          this.norm <- wArea[,-1] %>% 
               sapply(FUN = function(x) x/wArea[,grep(this.IS,
                                                      names(wArea))]) %>%
               as_data_frame %>% 
               mutate(`Replicate Name` = wArea$`Replicate Name`) %>%
               gather(MassFeature,Area_Norm, -`Replicate Name`)
          this.mean <- IS.means %>% filter(MassFeature==this.IS) %>% 
               select(ave) %>% as.numeric
          this.norm <- this.norm %>% mutate(Area_Norm = Area_Norm*this.mean)
          key <- ncol(area.norm)
          area.norm[,key+1] <- this.norm$Area_Norm
          names(area.norm)[key+1] <- paste(this.IS,"Norm.Area",sep=".")
          count <- length(which(!is.na(this.norm$Area_Norm)))/
               length(unique(this.norm$`Replicate Name`))
          print(paste(i, this.IS, count, sep="-"))
     }
}
glimpse(area.norm)
```

## break up the names
```{r, message=FALSE, warning=FALSE}
mydata_new <- area.norm %>% separate(`Replicate Name`, 
                                      c("runDate",
                                        "type","SampID","replicate"),"_") %>%
     mutate(Run.Cmpd = paste(area.norm$`Replicate Name`,area.norm$MassFeature))
binded <- binded %>% mutate(Run.Cmpd = paste(`Replicate Name`, MassFeature))

dat <- full_join(binded, mydata_new)
print(dat %>% select(runDate:replicate) %>% unique)
```
#Make a list of the internal standards, - the MIS, and RSD of pooled, RSD of smp for that
## curretnly set to use true pooled sample
```{r, message=FALSE, warning=FALSE}
cut.off <- 0.1

dat2 <- dat %>%
  filter(MassFeature %in% IS.dat$MassFeature,
         MassFeature != "Dil.Factor") %>%
  select(-(`Replicate Name`:Area))  %>%
  select(-(runDate:replicate)) %>%
  gather(key = "MIS", value = "Adjusted_Area", factor_key = TRUE, -Run.Cmpd) %>%
  left_join(dat %>% select(type, MassFeature, SampID, Run.Cmpd)) %>%
  mutate(Adjusted_Area = as.numeric(Adjusted_Area))

smpdat <- dat2 %>%
  filter(type == "Smp")%>%
  group_by(MassFeature, MIS) %>%
  summarise(RSD_ofSmp = sd(Adjusted_Area, na.rm = T)/mean(Adjusted_Area, na.rm = T))


TruePooGBTDat <- dat2 %>%
  filter(type == "Poo",
         SampID == "TruePooGBT") %>%
  group_by(MassFeature, MIS) %>%
  summarise(RSD_ofPoo = sd(Adjusted_Area, na.rm = T)/mean(Adjusted_Area, na.rm = T))

alldat <-   full_join(smpdat, TruePooGBTDat)

injectONlY <- alldat %>%
  filter(MIS == "Dil.Factor.Norm.Area" ) %>%
  mutate(Orig_RSD = RSD_ofPoo)%>%
  select(-RSD_ofSmp, -RSD_ofPoo, -MIS)

injectONlY_toPlot <- alldat %>%
  filter(MIS == "Dil.Factor.Norm.Area" ) 

newalldat <- left_join(alldat, injectONlY) %>%
  mutate(del_RSD = ( Orig_RSD - RSD_ofPoo),
         percRSD = del_RSD/Orig_RSD) %>%
  mutate(accept_MIS = (percRSD > cut.off)) #%>%
  # filter(MIS != "Acetyl CoA.Norm.Area")

# write.csv(newalldat,  paste0("../output/TargetedMetabolites/",column.id,"_IS_testResults.csv"))

g <- ggplot()+
  geom_point(dat = newalldat, shape = 21, color = "black", size = 2,aes(x = RSD_ofPoo, y = RSD_ofSmp, fill = accept_MIS))+ 
  scale_fill_manual(values=c("white","dark gray"))+
  geom_point(dat = injectONlY_toPlot, aes(x = RSD_ofPoo, y = RSD_ofSmp), size = 3) +
  facet_wrap(~ MassFeature)
g

# ggsave(paste0("../output/TargetedMetabolites/",column.id,"_IS_experiment_wPool.pdf"), plot = g, device = "pdf", width = 10, height = 10, units = "in")
```

#Make a summary of which internal standards were conidsterd "Acceptable" and "Best" Matching Internal Standards
```{r, message=FALSE, warning=FALSE, echo=FALSE}
#Makes data Long
longdat <- dat %>%
  filter(MassFeature != "Dil.Factor") %>%
   select(-(`Replicate Name`:Area))   %>%
  select(-(runDate:replicate)) %>%
  gather(key = "MIS", value = "Adjusted_Area", factor_key = TRUE, -Run.Cmpd) %>%
  left_join(dat %>% select(SampID, type, MassFeature, Run.Cmpd)) %>%
  mutate(Adjusted_Area = as.numeric(Adjusted_Area))

#Look only the Pooled samples, to get a lowest RSD of the pooled possible (RSD_ofPoo), then choose which IS reduces the RSD the most (Poo.Picked.IS)
poodat <- longdat %>%
  filter(type == "Poo",
         SampID == "TruePooGBT") %>%
  group_by(MassFeature, MIS) %>%
  summarise(RSD_ofPoo =  sd(Adjusted_Area, na.rm = T)/mean(Adjusted_Area, na.rm = T))

poodat <- poodat %>% left_join(poodat %>%
                                 group_by(MassFeature) %>%
                                 summarise(Poo.Picked.IS = unique(MIS)[which.min(RSD_ofPoo)][1]))

#Get the starting point of the RSD (Orig_RSD), calculate the change in the RSD, say if the MIS is acceptable
newpoodat <- left_join(poodat, poodat %>%
                         filter(MIS == "Dil.Factor.Norm.Area" ) %>%
                         mutate(Orig_RSD = RSD_ofPoo) %>%
                         select(-RSD_ofPoo, -MIS)) %>%
  mutate(del_RSD = (Orig_RSD - RSD_ofPoo)) %>%
  mutate(percentChange = del_RSD/Orig_RSD) %>%
  mutate(accept_MIS = (percentChange > cut.off & Orig_RSD > 0.1))  #HERE IS WHERE WE NEED TO DEFINE WHAT MAKES AND ACCEPTABLE MATCHED INTERNAL STANDARD

#Change the BMIS to "Dil.Factor.Norm.Area" if the BMIS is not an acceptable - Adds a column that has the BMIS, not just Poo.picked.IS
NoAMIS_newpoodat_BMIS <- newpoodat %>%
  filter(MIS == Poo.Picked.IS) %>% #Pulling out just the pooplus is matches
  filter(accept_MIS == "FALSE") %>%
  mutate(FinalBMIS = "Dil.Factor.Norm.Area") 

newpoodat_BMIS <- newpoodat %>%
              filter(MIS == Poo.Picked.IS) %>% 
              filter(accept_MIS == "TRUE") %>%
              mutate(FinalBMIS = Poo.Picked.IS) %>%
  bind_rows(NoAMIS_newpoodat_BMIS)

#Makes the full dataset from the fixed ones (where there is no AMIS)
FullDat_fixed <- left_join(newpoodat, newpoodat_BMIS %>%
                        select(MassFeature, FinalBMIS)) %>%
  filter(!is.na(accept_MIS))
FullDat_fixed <- FullDat_fixed %>% left_join(FullDat_fixed %>%
              filter(FinalBMIS == MIS) %>%
              mutate(FinalRSD = RSD_ofPoo) %>%
              select(MassFeature, FinalRSD))

#Only get MFs with FinalRSD < 0.2
Good_MFs <- FullDat_fixed %>%
  filter(MIS == Poo.Picked.IS) %>%
  filter(FinalRSD < 0.2)

#Get number of mass features
MassFeatures <- length(Good_MFs$MassFeature)
print("Total mass features")
print(MassFeatures)

 #This will give us the number of mass features that were picked as a BMIS for each IS
BMIS_percent <- Good_MFs %>%
  filter(FinalBMIS != "Dil.Factor.Norm.Area") %>%
  group_by(FinalBMIS) %>%
  summarise(MFs = n()) %>%
  mutate(PercentofBMIS = MFs/MassFeatures)  

BMIS_Summary2 <- Good_MFs %>%
  filter(FinalBMIS != "Dil.Factor.Norm.Area")
MassFeatures2 <- length(BMIS_Summary2$MassFeature)
print("Mass features with BMIS")
print(MassFeatures2)


#This will give us the number of mass features that were picked as an AMIS for each IS
AMIS_percent <- FullDat_fixed %>%
  filter(MassFeature %in% Good_MFs$MassFeature) %>%
  filter(accept_MIS == "TRUE") %>%
  group_by(FinalBMIS) %>%
  summarise(MFs = n()) %>%
  mutate(PercentofAMIS = MFs/MassFeatures)  #This gives us the % of the MF chosen by each IS 

Summary <- left_join(AMIS_percent %>% select(-MFs), BMIS_percent %>% select(-MFs)) %>%
  mutate(Originality_Index = PercentofBMIS/PercentofAMIS)
  
Summarylong <- left_join(AMIS_percent %>% select(-MFs), BMIS_percent %>%
                           select(-MFs))%>% 
  gather(key = "type", value = "Percent", -FinalBMIS)

g <- ggplot() +
  geom_col(data = Summarylong , aes(x = type, y = Percent))+
  facet_wrap(~FinalBMIS)

g

# write.csv(Summary, paste0("../output/TargetedMetabolites/",column.id,"_AMISvsBMIS.csv"),sep="")

# ggsave( paste0("../output/TargetedMetabolites/",column.id,"_AMISvsBMIS.pdf"), plot = g, device = "pdf", width = 10, height = 10, units = "in")

```
###Get all the data back - and keep only the MF-MIS match set for the BMIS
```{r, message=FALSE, warning=FALSE}
#Add a column to the longdat that has important information from the FullDat_fixed, then only return data that is normalized via B-MIS normalization
FullDat_fixed.update <- FullDat_fixed %>%
  mutate(FinalBMIS = ifelse(MassFeature == "Alanine", "DL-Alanine, D3 - IS.Norm.Area",
                      ifelse(MassFeature == "L-Alanine_13C-0 15N-0", "DL-Alanine, D3 - IS.Norm.Area",
                             
                      ifelse(MassFeature == "Histidine", "DL-Histidine, 15N - IS.Norm.Area",
                      ifelse(MassFeature == "L-Histidine_13C-0 15N-0", "DL-Histidine, 15N - IS.Norm.Area",

                      ifelse(MassFeature == "Proline", "DL-Proline, D7 - IS.Norm.Area",                      
                      ifelse(MassFeature == "L-Proline_13C-0 15N-0", "DL-Proline, D7 - IS.Norm.Area",

                      ifelse(MassFeature == "Valine", "DL-Valine, D8 - IS.Norm.Area", 
                      ifelse(MassFeature == "L-Valine_13C-0 15N-0", "DL-Valine, D8 - IS.Norm.Area", 
                             
                      ifelse(MassFeature == "Isoleucine", "L-Isoleucine, 15N - IS.Norm.Area",  
                      ifelse(MassFeature == "L-Isoleucine_13C-0 15N-0", "L-Isoleucine, 15N - IS.Norm.Area",
                             
                      ifelse(MassFeature == "Leucine", "L-Isoleucine, 15N - IS.Norm.Area",   
                      ifelse(MassFeature == "L-Leucine_13C-0 15N-0", "L-Isoleucine, 15N - IS.Norm.Area",  
                             
                      ifelse(MassFeature == "Methionine", "L-Methionine, D3 - IS.Norm.Area",
                      ifelse(MassFeature == "L-Methionine_13C-0 15N-0", "L-Methionine, D3 - IS.Norm.Area",
                             
                      ifelse(MassFeature == "Adenine", "Adenine, 15N2 - IS.Norm.Area",
                      ifelse(MassFeature == "Adenine_13C-0 15N-0", "Adenine, 15N2 - IS.Norm.Area",
                             
                      ifelse(MassFeature == "Cytosine", "Cytosine, 13C2-15N3 - IS.Norm.Area",
                      ifelse(MassFeature == "Cytosine_13C-0 15N-0", "Cytosine, 13C2-15N3 - IS.Norm.Area",
                             
                      ifelse(MassFeature == "Guanine", "Guanine, 13C-15N2 - IS.Norm.Area",
                      ifelse(MassFeature == "Guanine_13C-0 15N-0", "Guanine, 13C-15N2 - IS.Norm.Area",
                             
                      ifelse(MassFeature == "Arsenobetaine", "Arsenobetaine, 13C2 - IS.Norm.Area",
                      ifelse(MassFeature == "Arsenobetaine_13C-0 15N-0", "Arsenobetaine, 13C2 - IS.Norm.Area",
                             
                             
                      ifelse(MassFeature == "AMP", "Adenosine Monophosphate, 15N5 - IS.Norm.Area",
                      ifelse(MassFeature == "AMP_13C-0 15N-0", "Adenosine Monophosphate, 15N5 - IS.Norm.Area",
                      ifelse(MassFeature == "GMP", "Guanosine Monophosphate, 15N5 - IS.Norm.Area",
                      ifelse(MassFeature == "GMP_13C-0 15N-0", "Guanosine Monophosphate, 15N5 - IS.Norm.Area",
                      ifelse(MassFeature == "Sucrose", "Sucrose, 13C - IS.Norm.Area",
                      ifelse(MassFeature == "Sucrose_13C-0 15N-0", "Sucrose, 13C - IS.Norm.Area",
                      ifelse(MassFeature == "Trehalose", "Trehalose, 13C - IS.Norm.Area",
                      ifelse(MassFeature == "Trehalose_13C-0", "Trehalose, 13C - IS.Norm.Area",
                      ifelse(MassFeature == "Sulfoacetic Acid", "Sulfoacetic Acid, 13C2 - IS.Norm.Area",
                      ifelse(MassFeature == "Sulfoacetic Acid_13C-0 15N-0", "Sulfoacetic Acid, 13C2 - IS.Norm.Area",
                      ifelse(MassFeature == "Isethionic acid", "Isethionic Acid, 13C2 - IS.Norm.Area",
                      ifelse(MassFeature == "Isethionic acid_13C-0 15N-0", "Isethionic Acid, 13C2 - IS.Norm.Area",
                              ifelse(MassFeature == "Isethionic acid_13C-0", "Isethionic Acid, 13C2 - IS.Norm.Area",
                      ifelse(MassFeature == "Succinic acid", "Succinic Acid, D4 - IS.Norm.Area",
                      ifelse(MassFeature == "Succinic acid_13C-0 15N-0", "Succinic Acid, D4 - IS.Norm.Area",
                      ifelse(MassFeature == "L-Cysteic acid", "L-Cysteic Acid, D3 - IS.Norm.Area",
                      ifelse(MassFeature == "L-Cysteic acid_13C-0 15N-0", "L-Cysteic Acid, D3 - IS.Norm.Area",
                             
                      ifelse(MassFeature == "Sulfolactic acid", "Sulfolactic Acid, 13C3 - IS.Norm.Area",
                      ifelse(MassFeature == "Sulfolactic acid_13C-0 15N-0", "Sulfolactic Acid, 13C3 - IS.Norm.Area",
                      # ifelse(MassFeature == "Taurine", "Taurine - IS.Norm.Area",
                      # ifelse(MassFeature == "Taurine_13C-0 15N-0", "Taurine - IS.Norm.Area",
                             FinalBMIS)))))))))))))))))))))))))))))))))))))))
                      # ))
))) %>%
  filter(MassFeature != "Inj_vol" )


BMIS_normalizedData <- FullDat_fixed.update %>%
  filter(MIS == FinalBMIS) %>%
  mutate(FinalRSD = RSD_ofPoo) %>%
  select(MassFeature, Orig_RSD, del_RSD, percentChange, FinalBMIS, FinalRSD) %>%
  right_join(longdat) %>%
  filter(MIS == FinalBMIS) %>%
  left_join(., dat %>% select(Run.Cmpd, runDate, type, SampID, replicate, Area)) %>%
  rename(OriginalArea = Area)

new.filename = paste0(str_sub(filename,1,-5),"_BMISed.csv")
write.csv(BMIS_normalizedData, file = new.filename)
print(paste("Your BMIS results are saved as", new.filename))
print("The output of the B-MIS normalized data is in the column named Adjusted Area")
```

```{r write out the model matches}
BMIS.model <- BMIS_normalizedData %>%
  dplyr::select(MassFeature, FinalBMIS) %>%
  unique()
write_csv(BMIS.model, paste0("../output/TargetedMetabolites/",column.id, "_BMIS Model.csv"))

BMIS.multiplier <- BMIS_normalizedData %>%
  filter(MassFeature %in% unique(IS.dat$MassFeature)) %>%
  select(OriginalArea, MassFeature, SampID, type, replicate, runDate) %>%
  unique() %>%
  full_join(.,IS.means) %>%
  filter(!is.na(type)) %>%
  dplyr::rename(IS.ave = ave) %>%
  mutate(BMIS.multiplier = ((1/OriginalArea)*(IS.ave)),
         FinalBMIS =  paste(MassFeature,"Norm.Area",sep=".")) %>%
  ungroup() %>%
  dplyr::select(-MassFeature, -OriginalArea, -IS.ave)

write_csv(BMIS.multiplier, paste0("../output/TargetedMetabolites/",column.id, "_BMIS_multipliers.csv"))

```

